Sweat electrolytes and CFTR activity in the era of CFTR modulators

### 2025-08-15 Edith Zemanick/Sweat Variability/sweat_test_analysis.qmd
genotype risk ROC curves, etc.

```{r setup}
#| include: false
library(knitr)
library(Hmisc)
library(lubridate)
library(readxl)
library(tidyverse)
library(arsenal)
library(pROC)
home_dir <- switch(
    Sys.info()["sysname"],
    "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Edith Zemanick/Sweat Variability",
    "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF/Edith Zemanick/Sweat Variability",
    "Linux" = "/home/tim/OneDrive/Vigers/CF/Edith Zemanick/Sweat Variability"
)
github_dir <- switch(
    Sys.info()["sysname"],
    "Darwin" = "/Users/tim/Documents/GitHub",
    "Windows" = "C:/Users/Tim/Documents/GitHub",
    "Linux" = "/home/tim/Documents/GitHub"
)
source(paste0(github_dir, "/CF/genotype_class_severity.R"))
knitr::opts_knit$set(root.dir = home_dir)
```

@@

df <- left_join(df, method)

@@

@@

@@

@@

### Individual ROC Curves

@@

>>>>

```{r setup}
#| include: false
library(knitr)
library(Hmisc)
library(lubridate)
library(readxl)
library(tidyverse)
library(arsenal)
library(pROC)
home_dir <- switch(Sys.info()["sysname"],
    "Darwin" = "/Users/tim/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF/Edith Zemanick/Sweat Variability",
    "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF/Edith Zemanick/Sweat Variability",
    "Linux" = "/home/tim/OneDrive/Vigers/CF/Edith Zemanick/Sweat Variability"
)
github_dir <- switch(Sys.info()["sysname"],
    "Darwin" = "/Users/tim/Documents/GitHub",
    "Windows" = "C:/Users/Tim/Documents/GitHub",
    "Linux" = "/home/tim/Documents/GitHub"
)
source(paste0(github_dir, "/CF/genotype_class_severity.R"))
knitr::opts_knit$set(root.dir = home_dir)
```

@@

df <- left_join(df, method) %>% arrange(Name, desc(Method))

@@

df <- df[-which(duplicated(df$Name)), ]

@@

# Data Cleaning

- Started with 5,046 sweat tests with 4,646 unique individuals.
- 1,551 did not have demographics available.
- 399 with Cl < 10 and 1 with Cl > 160
- 156 with Na < 10
- 19 over age 50 and 3 under age 2 days
- 43 with insufficient quantity 
- 25 on modulators

@@

### By Diagnosis

@@

#### Individual ROC Curves

@@

### By genotype risk

```{r}
# Fit a multiclass ROC
gr_roc <- roc(
    `Genotype Risk` ~ `Na:Cl`,
    data = df,
    levels = c("Mild", "Severe"),
    quiet = T
)
plot(
    gr_roc,
    print.auc = T,
    print.thres = T,
    main = "Mild vs. Severe Genotype"
)
kable(coords(
    gr_roc,
    "best",
    best.method = "youden",
    ret = c(
        "threshold",
        "sensitivity",
        "specificity",
        "accuracy",
        "tpr",
        "fpr",
        "tnr",
        "fnr"
    )
))
```
